---
title: "reprex"
author: "Allison Horst"
date: "8/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```

Your job is to identify an error, then make a reproducible example that would help future you or someone else understand how to write the code correctly. In other words, your reprex code will *work* and offer a solution to the error thrown in each of the following examples. 

Data are in `AS00601.csv` (and read in correctly below as `mack_creek_vertebrates`). 

Data package title: Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present

**Citation:** Gregory, S.V. and I. Arismendi. 2020. Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present ver 14. Environmental Data Initiative. https://doi.org/10.6073/pasta/7c78d662e847cdbe33584add8f809165

### Read in the data 

There are no problems here. 
```{r}
mack_creek_vertebrates <- read_csv(here("AS00601.csv"))
```

### reprex 1

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 1: 
mack_creek_lengths <- mack_creek_vertebrates %>% 
  clean_names() %>% 
  select(year:sampledate) %>% 
  filter(section == "CC") %>% 
  mutate(across(where(is.character, tolower))) %>% 
  drop_na(species) %>% 
  group_by(species) %>% 
  summarize(mean_length_cm = mean(length1, na.rm = TRUE),
            sd_length_cm = sd(length1, na.rm = TRUE)) %>% 
  ungroup()
```

```{r}
library(tidyverse)
library(reprex)
library(dplyr)

df_1 <- tribble(
  ~species, ~common_name, ~dbh,
  "Quercus suber", "Cork oak", 8.2,
  "Lynothamnus floribundus", "Catalina Ironwood", 2.6,
  "Pinus torreyana", "Torrey pine", 26.9
  )

# Example 1 is throwing an error because the code line to mutate all characters to lower case is missing a parenthesis after "as.character".

# df <- df_1 %>% mutate(across(where(is.character, tolower))

df_fixed <- df_1 %>% 
  mutate(across(where(is.character), tolower))

```


### reprex 2

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 2:
mack_creek_vertebrates %>% 
  clean_names() %>% 
  filter(species == "ONCL") %>% 
  ggplot(aes(x = length1, y = weight)) +
         geom_point(aes(shape = 12), color = "purple") +
         theme_minimal() +
         labs(x = "Cutthroat trout length (cm)",
              y = "Weight (g)")
```

```{r}
library(tidyverse)
library(reprex)

df2 <- tribble(
  ~common_name, ~species_name, ~total_count,
  "white sage", "salvia apiana", 300,
  "black sage", "salvia mellifera", 1000,
  "pitcher sage", "lepechinia fragrans", 20,
)

# Example 2 - ggplot code was throwing an error in the geom_point code line as the aesthetic size was mis-typed as 'shape' instead of 'size'. 

# Error line: geom_point(aes(shape = 12), color = "purple") 

df2_fixed <- df2 %>% 
  ggplot(aes(x = common_name, y = species_name)) +
  geom_point(aes(size = 12), color = "purple")

```



## End